[dcpo_gender_roles]: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles

### 2020-10-19 paper/dcpo_gender_roles.Rmd
add lines

This article proceeds with the following order. First, we

# Multi-Dimensionality of Egalitarian Gender Role

>>>>

This article proceeds with the following order. First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector. Next, we illustrate the data source we used to build our index. Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced. Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.

# Multi-Dimensionality in Egalitarian Gender Role
